\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-24 paper.tex
3.4 revised

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(est) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\hline
\multirow{3}{*}{$d\!=\!(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{a BA demand $d$, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs} \\
\hline
$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived and admitted demands\footnote{When an admitted demand finishes, it will be removed from $\hat{D}$.} }\\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
%\hline
%$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$\hat{D}$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$\mathbf{b}^k_d$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$c_e, c_t$ &\multicolumn{6}{|l}{the remaining capacity on link $e$ or a tunnel $t$}\\
\hline
$\mathbf{z}\in Z$ &\multicolumn{6}{|l}{a network failure scenario in the scenario set}\\
\hline
$p_{\mathbf{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\mathbf{z}$ occurs}\\
\hline
$v_t^{\mathbf{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\mathbf{z}$}\\
 \hline
  $L_e^{ \mathbf{z}}$ &\multicolumn{6}{|l}{whether link $e$ is available under scenario $ \mathbf{z}$}\\
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

&\textbf{Output Variables}\\
\hline
$g_d$& \multicolumn{6}{|l}{whether demand $d$ is admitted}\\
\hline
%$f_{d}^t$& \multicolumn{6}{|l}{bandwidth allocated for the $i$-th demand over tunnel $t \in T_{k}$ }\\
$f_d^t$& \multicolumn{6}{|l}{bandwidth allocated for demand $d$ over tunnel $t$}\\
\hline
$h_d$& \multicolumn{6}{|l}{profit (after refunding)  for demand $d$}\\
%\hline
%\hline
%&\textbf{Auxiliary Output Variables}\\
%\hline
%% $S_j$ &\multicolumn{6}{|l}{Network service achieved availability of $j$}\\
%%\hline
% $A_d^{\mathbf{z}}$&\multicolumn{6}{|l}{Whether scenario $\mathbf{z}$ is safe or not for $i$ }\\
% \hline
% $S_i$&\multicolumn{6}{|l}{Achieved availability of $i$ }\\
\bottomrule
\bottomrule
\end{tabular}
\end{table}

@@

%\subsection {Traffic Engineering for Diverse Availability Targets }\label{BATE}
%Based on the the network scenarios, we design our traffic engineering algorithm that optimizes bandwidth-based availability for diverse services.
%To this end, we introduce the problem formulation of $\mathsf{BATE}$ problem and 
 \begin{algorithm}
\KwIn{Input parameters shown in Table \ref{Notation}} 
\KwOut{Whether the new demand can be admitted.}
%$g_d=0, s_d=1, \forall d \in D$; \\
%$f_{d}^t = 0, \forall d \in D ,  k\in K: t\in T_{k}$;\\
\While{$true$}{
$d=\arg_{d'\in D}min\{\sum_{k\in K}b_{d'}^k\times \beta_{d'}\}$;\\
\For{$k\in K$}{
\If{$b_{d}^k >$  remaining capacity of s-d pair $k$}{
    \Return $ False$;\\
}
$T'_k=T_k$;\\
\While{$b_{d}^k>0$}{
$t=\arg_{t\in T'_k}{\min\{c_t*p_t\}}$;\\
 $f_{d}^t=\min$\{$c_t$, $b_{d}^k$\};\\
$ T'_k=T'_k \setminus t$;\\
 $s_d=s_d*p_t$;\\
 $b_{d}^k = b_{d}^k- f_{d}^t;$\\
  $c_t= c_t- f_{d}^t;$\\
}
%\For{$t\in T_k$}{
%   $f_{d}^t=Allocation(t, \mathbf{b}^k_d)$;\\
%   \If{$f_{d}^t>=0$}{
%   $s_i=s_i*p_t$;\\
%   $\mathbf{b}^k_d = \mathbf{b}^k_d- f_{d}^t;$\\
%   }
%   \If{$\mathbf{b}^k_d<=0$}{
%   \textbf{break};\\
%   }
%}
}
  \If{$s_d <   \beta_{d}$}{
      \Return $False$;\\
  }
  $D=D\setminus d$;\\
}

@@

\begin{theorem}\label{NP-222}
If a new demand $d$ can be admitted by Algorithm \ref{greedy-1}, 
there must exist an allocation strategy to satisfy the bandwidth availability targets of all demands $D=\hat{D} \cup {d}$.
\end{theorem} 
%\begin{proof}
%We use the contradiction method to prove, i.e., there is a demand that is admitted by Algorithm \ref{greedy-1} but the network is unable to satisfy its bandwidth-based availability.
%There are two cases: (i) network bandwidth is insufficient; (ii) The availability provided by the network is not enough. 
%Case (i) is impossible, because if bandwidth is insufficient (i.e., $\mathbf{b}^k_d> Capacity (T_k)$) , Algorithm \ref{greedy-1} won't admit the demand (Line 6-8).
%Case (ii) is also impossible, because if the availability is smaller than its target (i.e., $s_i <   \beta_{\gamma_{i}}$) , Algorithm \ref{greedy-1} will reject the demand (Line 14-16).
%This completes the proof. 
%\end{proof}
%We can reduce the NP-hard all-or-nothing multi-commodity flow problem \cite{inproceedings2} to a special case of admission control problem, and the detailed proof can be found in Appendix \ref{appendix1}.

@@

\subsection{Failure recovery} \label{backup}
In $\mathsf{BATE}$,  traffic can also be redistributed across the surviving tunnels via rerouting when any tunnel becomes unavailable.
%Previous tunnel-based traffic engineering schemes (such as FFC) keep link utilization low to prevent congestion when there are failures.
%Different from them, links have less vacant capacity under $\mathsf{BATE}$, therefore, when there are failures, re-routing might cause congestion.
%When a link $e'$ fails, all tunnels through this link  fails.
In reality, service providers have to derive refunding credits for violating availability targets (see $\S$\ref{background}).
$\mathsf{BATE}$ proactively considers failure scenarios and pre-computes backup allocation to maximize total revenue, and the surviving tunnels can be used immediately to support tenants.
%Each tunnel belongs to one flow pair.
%We can divide all node pairs into two groups, i.e.,  victim node pairs and normal node pairs, which is similar to \cite{sentinel}.
%Let $H$ denote all the victim node pairs when link $e'$ fails.
%Assume link $e'$ will fail, the normal tunnel set is $Q_{k}$ and the backup tunnel set is $Q'_{k}$.
%In reality, the backup tunnel set can be pre-computed by the network operators beforehand.
For example, Figure \ref{recovery} shows two services are from DC1 to DC4 and both of them need bandwidth demand of 2.
Link capacity is 1 everywhere.
Figure \ref{recovery}(a) shows the original traffic engineering allocation and it is used when no failures happen.
%if we assume the link between DC2 and DC4 is down, then DC1$\to$DC4 is victim node pair and DC1$\to$ DC2 is normal pair. 
%the backup tunnel set $Q'$=\{DC1$\to$DC2$\to$DC3$\to$DC4\} and normal tunnel set is 
%$Q$ =\{DC1$\to$DC3$\to$DC4\} for the victim node pair DC1$\to$DC4.
%Let $M_e$ denote the used bandwidth of link $e$ by normal node pairs,
Figure \ref{recovery}(b) depicts the backup allocation result when we assume the link between DC2 and DC4 is down, and the result will be put into practice when link DC2 $\to$ DC4 failure is detected.
Network scenario number is huge for large-scale network and we assume that at any time, only one link in the network could fail. 
If we assume network scenario $ \mathbf{z}$ could happen, and let 
%$f^{\mathbf{z}}_{ikt}$ denote bandwidth of $i$ over tunnel $t\in T^{ \mathbf{z}}_k$, where 
$T^ { \mathbf{z}}_k$ denote the surviving tunnel set under scenario $ \mathbf{z}$ and the bandwidth allocated for demand $d$ over tunnel $t$ should be non-negative, i.e.,
\begin{equation}
f^{t}_{d} \ge 0, \quad\forall d \in D ,  k\in K : t\in T^{\mathbf{z}}_k.
\label{constraint-f3}
\end{equation}

Let $L_e^{ \mathbf{z}}$ denote whether link $e$ is available under scenario $ \mathbf{z}$.
The total bandwidth should be smaller than capacity for each available link, i.e.,

\begin{figure}[t]
\centering
\subfigure[Original TE allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-1.pdf}}
\subfigure[Backup allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-2.pdf}}
\caption{There are two services from DC1 to DC4 and link capacity is 1 everywhere. (a) shows the original TE allocation. (b) shows the backup allocation result when assuming link DC2 $\to$ DC4 is broken.  }
\label{recovery}
\end{figure}
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-recovery}
% &maximize  \sum_{i\in I_a} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
%\sum_{i\in I_a}\sum_{k\in K}\sum_{t\in Q_{h}} f'_{ikt}u_t^e+ \sum_{i\in I_a}\sum_{k\in K}\sum_{t'\in Q_{h}} f''_{ikt'}L_{t'e} \le c_e, &\text{$\forall e \in E \setminus e' $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

\begin{small}
\begin{eqnarray} \label{B-constraint}
\sum_{d\in \hat{D}}\sum_{k\in K:t\in T^{ \mathbf{z}}_k} f^{t}_{d}u_t^e \le c_e \times L_e^{ \mathbf{z}}
\end{eqnarray}
\end{small}

The revenue return for $i$ over node pair $k$ can be described:
\begin{small}
\begin{eqnarray} \label{B-return}
R_{dk}=\frac{\sum_{t\in T^{ \mathbf{z}}_k} f^{t}_{d}}{\mathbf{b}^k_d}, \forall  d \in \hat{D},  k \in K
\end{eqnarray}
\end{small}

If the allocated bandwidth  of BA demand $d$ between each node pair is larger than its need (i.e., $R_{dk} \ge 1, \forall d \in  \hat{D}$), the profit unit is 1, 
%If it is between $\beta_j^{k}$ and $\beta_j^{k+1}$, then the profit is $\alpha_j^k$, where $1>\alpha_j^1>\alpha_j^2>...>\alpha_j^k$.
otherwise, there is a refunding, which can be derived from SLA and we use $\mu_{d}$ to denote its profit fraction after refunding.
Then, the profit of $d$ is:

\begin{equation}
\forall  d \in \hat{D} : h_d=
\begin{cases}
1 &\text{$\forall k \in K: R_{dk} \ge 1 $}\\
\mu_{d} &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation}

It is a step function and we can change it to the following linear format :

\begin{equation}
\begin{cases}
h_d=y_d+\mu_{d}*(1-y_d),&{\forall d \in \hat{D}.} \\
R_{dk} < M*y_d+1-y_d,&{\forall d \in \hat{D},  k\in K.} \\
R_{dk} >= y_d,&{\forall d \in \hat{D},  k\in K.} \\
y_d \in\{0,1\},&{\forall d \in \hat{D}.} \\
\end{cases}
\label{A-SSS2}
\end{equation}

Where $M$ is a big integer that is at least larger than the upper bound of $R_{dk}$.
Let $w_d$ denote the profit of demand $d$ when its availability target can be satisfied.
The goal of failure recovery is to maximize profits of all the admitted demands, and we can give the problem formulation finally:

\begin{equation}
\small
\begin{aligned} \label{BATE-recovery}
 &maximize  \sum_{d\in \hat{D}} w_d\times h_d\\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t.  (\ref{constraint-f3}), (\ref{B-constraint}), (\ref{B-return}), (\ref{A-SSS2})
\end{array}
\end{aligned}
\end{equation}

The auxiliary output variables $y_d$ are chosen from \{0,1\},  so that the  failure recovery problem is a 0-1 Mixed-integer linear programming.

\begin{lemma}\label{NP-hard}
The failure recovery problem is NP-hard.
\end{lemma}
The detailed proof can be found in Appendix \ref{appendix1}.

As the failure recovery problem is NP-hard and one important question is \textit{can we develop an efficient algorithm to solve it in polynomial time?} 
%For the second challenge, although the powerful mathematical optimization solver such as Gurobi \cite{gurobi} can derive the solution, it might be too slow to converge before next TE scheduling epoch.
In this case,  we propose a greedy algorithm to attain an approximate solution whose pseudocode is shown in Appendix \ref{B}.
The key idea of the greedy algorithm is to give priority to demands in non-decreasing order by the ratio of profit to its efficient bandwidth demands.
\textit{We also prove the approximation of the greedy algorithm is 2  in Appendix \ref{B}}. 
%The greedy algorithm can solve $\mathsf{BATE}$  problem in  $O(|J||Z||T_k||E|)$ time.
%We further explore the accuracy of greedy algorithm in Section \ref{evaluation}.

>>>>

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(est) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\hline
\multirow{3}{*}{$d\!=\!(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{a BA demand $d$, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs} \\
\hline
$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived and admitted demands\footnote{When an admitted demand finishes, it will be removed from $\hat{D}$.} }\\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
%\hline
%$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$\hat{D}$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$\mathbf{b}^k_d$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$c_e, c_t$ &\multicolumn{6}{|l}{the remaining capacity on link $e$ or a tunnel $t$}\\
\hline
$\mathbf{z}\in Z$ &\multicolumn{6}{|l}{a network failure scenario in the scenario set}\\
\hline
$p_{\mathbf{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\mathbf{z}$ occurs}\\
\hline
$v_t^{\mathbf{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\mathbf{z}$}\\
 \hline
$w_e^{ \mathbf{z}}$ &\multicolumn{6}{|l}{whether link $e$ is available under scenario $ \mathbf{z}$}\\
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

&\textbf{Output Variables}\\
\hline
$g_d$& \multicolumn{6}{|l}{whether demand $d$ is admitted}\\
\hline
%$f_{d}^t$& \multicolumn{6}{|l}{bandwidth allocated for the $i$-th demand over tunnel $t \in T_{k}$ }\\
$f_d^t$& \multicolumn{6}{|l}{bandwidth allocated for demand $d$ over tunnel $t$}\\
\hline
$r_d$& \multicolumn{6}{|l}{profit (after refunding)  for demand $d$}\\
%\hline
%\hline
%&\textbf{Auxiliary Output Variables}\\
%\hline
%% $S_j$ &\multicolumn{6}{|l}{Network service achieved availability of $j$}\\
%%\hline
% $A_d^{\mathbf{z}}$&\multicolumn{6}{|l}{Whether scenario $\mathbf{z}$ is safe or not for $i$ }\\
% \hline
% $S_i$&\multicolumn{6}{|l}{Achieved availability of $i$ }\\
\bottomrule
\bottomrule
\end{tabular}
\end{table}

@@

%\subsection {Traffic Engineering for Diverse Availability Targets }\label{BATE}
%Based on the the network scenarios, we design our traffic engineering algorithm that optimizes bandwidth-based availability for diverse services.
%To this end, we introduce the problem formulation of $\mathsf{BATE}$ problem and 
 \begin{algorithm}
\KwIn{Input parameters shown in Table \ref{Notation}} 
\KwOut{Whether the new demand can be admitted.}
%$g_d=0, s_d=1, \forall d \in D$; \\
%$f_{d}^t = 0, \forall d \in D ,  k\in K: t\in T_{k}$;\\
\While{$true$}{
$d=\arg_{d'\in D}min\{\sum_{k\in K}b_{d'}^k\times \beta_{d'}\}$;\\
\For{$k\in K$}{
\If{$b_{d}^k >$  remaining capacity of s-d pair $k$}{
    \Return $ False$;\\
}
$T'_k=T_k$;\\
\While{$b_{d}^k>0$}{
$t=\arg_{t\in T'_k}{\min\{c_t*p_t\}}$;\\
 $f_{d}^t=\min$\{$c_t$, $b_{d}^k$\};\\
$ T'_k=T'_k \setminus t$;\\
 $s_d=s_d*p_t$;\\
 $b_{d}^k = b_{d}^k- f_{d}^t;$\\
  update the remaining capacities of links and tunnels;\\
  %$c_t= c_t- f_{d}^t;$\\
}
%\For{$t\in T_k$}{
%   $f_{d}^t=Allocation(t, \mathbf{b}^k_d)$;\\
%   \If{$f_{d}^t>=0$}{
%   $s_i=s_i*p_t$;\\
%   $\mathbf{b}^k_d = \mathbf{b}^k_d- f_{d}^t;$\\
%   }
%   \If{$\mathbf{b}^k_d<=0$}{
%   \textbf{break};\\
%   }
%}
}
  \If{$s_d <   \beta_{d}$}{
      \Return $False$;\\
  }
  $D=D\setminus d$;\\
}

@@

\begin{theorem}\label{NP-222}
If a new demand $d$ can be admitted by Algorithm \ref{greedy-1}, then
there must exist an allocation result $\{f_d^t\}$ to satisfy the bandwidth availability targets of all demands $D=\hat{D} \cup {d}$.
\end{theorem} 
%\begin{proof}
%We use the contradiction method to prove, i.e., there is a demand that is admitted by Algorithm \ref{greedy-1} but the network is unable to satisfy its bandwidth-based availability.
%There are two cases: (i) network bandwidth is insufficient; (ii) The availability provided by the network is not enough. 
%Case (i) is impossible, because if bandwidth is insufficient (i.e., $\mathbf{b}^k_d> Capacity (T_k)$) , Algorithm \ref{greedy-1} won't admit the demand (Line 6-8).
%Case (ii) is also impossible, because if the availability is smaller than its target (i.e., $s_i <   \beta_{\gamma_{i}}$) , Algorithm \ref{greedy-1} will reject the demand (Line 14-16).
%This completes the proof. 
%\end{proof}
%We can reduce the NP-hard all-or-nothing multi-commodity flow problem \cite{inproceedings2} to a special case of admission control problem, and the detailed proof can be found in Appendix \ref{appendix1}.

@@

\subsection{Failure recovery} \label{backup}
When failures occur and any tunnel becomes unavailable, traffic can be redistributed across the surviving tunnels. To reduce recovery time, $\mathsf{BATE}$ proactively computes backup allocation strategies for potential failure scenarios, so that the surviving tunnels can be used immediately, and packet loss 
can be mitigated \footnote{Here we only consider backup allocations for one link, while this scheme can be easily extended to deal with concurrent failures.}. 
%Previous tunnel-based traffic engineering schemes (such as FFC) keep link utilization low to prevent congestion when there are failures.
%Different from them, links have less vacant capacity under $\mathsf{BATE}$, therefore, when there are failures, re-routing might cause congestion.
%When a link $e'$ fails, all tunnels through this link  fails.

%Each tunnel belongs to one flow pair.
%We can divide all node pairs into two groups, i.e.,  victim node pairs and normal node pairs, which is similar to \cite{sentinel}.
%Let $H$ denote all the victim node pairs when link $e'$ fails.
%Assume link $e'$ will fail, the normal tunnel set is $Q_{k}$ and the backup tunnel set is $Q'_{k}$.
%In reality, the backup tunnel set can be pre-computed by the network operators beforehand.
For example, in Figure \ref{recovery}, there are two users, and the link capacity is 1 everywhere.  One user requests a bandwidth of 1 from DC1 to DC2, while the other one requests a bandwidth of 1 from DC1 to DC4.
Figure \ref{recovery}(a) shows the original bandwidth allocation when no failures occur, 
%if we assume the link between DC2 and DC4 is down, then DC1$\to$DC4 is victim node pair and DC1$\to$ DC2 is normal pair. 
%the backup tunnel set $Q'$=\{DC1$\to$DC2$\to$DC3$\to$DC4\} and normal tunnel set is 
%$Q$ =\{DC1$\to$DC3$\to$DC4\} for the victim node pair DC1$\to$DC4.
%Let $M_e$ denote the used bandwidth of link $e$ by normal node pairs,
and Figure \ref{recovery}(b) depicts the backup allocation pre-computed for a failure of link DC2$\to$DC4.
%and the result will be put into practice when link DC2 $\to$ DC4 failure is detected.

However, service providers have to refund credits to users if their bandwidth availability targets according the agreed SLAs are violated (see $\S$\ref{background}), both for users affected \textit{directly} by the failure and for users \textit{collaterally} affected by the recovery procedure. 
Our failure recovery scheme takes this economic factor into account in the way as follows.

\begin{figure}[t]
\centering
\subfigure[Original allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-1.pdf}}
\subfigure[Backup allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-2.pdf}}
%\caption{There are two services from DC1 to DC4 and link capacity is 1 everywhere. (a) shows the original TE allocation. (b) shows the backup allocation result when assuming link DC2 $\to$ DC4 is broken.  }
\caption{Pre-compute Backup allocation for link failure on DC2$\to$DC4}
\label{recovery}
\end{figure}
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-recovery}
% &maximize  \sum_{i\in I_a} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
%\sum_{i\in I_a}\sum_{k\in K}\sum_{t\in Q_{h}} f'_{ikt}u_t^e+ \sum_{i\in I_a}\sum_{k\in K}\sum_{t'\in Q_{h}} f''_{ikt'}L_{t'e} \le c_e, &\text{$\forall e \in E \setminus e' $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

For a given network scenario $ \mathbf{z}$ (where one link failure occurs) in consideration, 
%let
%$f^{\mathbf{z}}_{ikt}$ denote bandwidth of $i$ over tunnel $t\in T^{ \mathbf{z}}_k$, where 
%$T^ { \mathbf{z}}_k$ denote the set of surviving tunnels for the s-d pair $k$ under scenario $ \mathbf{z}$.
the ration of allocated bandwidth to a user's demanded bandwidth is \footnote{This is the same as equation (3), but we omit the superscript $\mathbf{z}$ of $R_{dk}^\mathbf{z}$.}
\begin{small}
\begin{eqnarray} \label{B-return}
R_{dk}}=\frac{\sum_{t\in T_k f^{t}_{d} v_t^{\mathbf{z}}} {\mathbf{b}^k_d}, \quad \forall  d \in \hat{D},  k \in K
\end{eqnarray}
\end{small}

If for every $k$, $R_{dk}$ is larger than its demand (i.e., $R_{dk} \ge 1$), 
then there is no problem since the demanded availability is still satisfied. 
However, if any $R_{dk}$ falls below 1, then the corresponding SLA will be violated. 
For simplicity, here we assume a simple pricing and refunding model, 
where the charge for serving a user demand $d$ is $g_d$, and if the SLA is violated, 
a fraction $\mu_d$ of $g_d$ will be refunded. 
We use $r_d$ denote the profit of demand $d$ with rufunding, such that

%If it is between $\beta_j^{k}$ and $\beta_j^{k+1}$, then the profit is $\alpha_j^k$, where $1>\alpha_j^1>\alpha_j^2>...>\alpha_j^k$.

\begin{equation*}
r_d=
\begin{cases}
g_d &\text{$\forall k \in K: R_{dk} \ge 1 $}\\
\(1-mu_{d})g_d &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation*}

We use an auxiliary integer variable $y_d \in \{0, 1\}$ to denote the violation condition, 
where $y_d=1$ means no violation. 
Then the profit $r_d$ can be rewritten as 
\begin{equation}
\label{A-SSS2}
\begin{array}{rclr}
y_d &\in &\{0,1\} &{\forall d \in \hat{D}} \\
r_d & = & g_d \times \Big(y_d+(1-\mu_{d})\times (1-y_d)\Big) &{\forall d \in \hat{D}} \\
R_{dk}& < & M\times y_d+1-y_d &{\forall d \in \hat{D},  k\in K} \\
R_{dk}& \ge &  y_d, &{\forall d \in \hat{D},  k\in K}
\end{array}
\end{equation}
where $M$ is a constant large enough (e.g., at least larger than the upper bound of $R_{dk}$).

\iffalse
\begin{equation}
\begin{cases}
h_d=y_d+\mu_{d}*(1-y_d),&{\forall d \in \hat{D}.} \\
R_{dk} < M*y_d+1-y_d,&{\forall d \in \hat{D},  k\in K.} \\
R_{dk} >= y_d,&{\forall d \in \hat{D},  k\in K.} \\
y_d \in\{0,1\},&{\forall d \in \hat{D}.} \\
\end{cases}
\label{A-SSS2}
\end{equation}
\fi

Besides, the bandwidth allocation result $f_t^d$ should be nonnegative
and limited by the available network capacity. 
Let $w_e^{ \mathbf{z}}$ denote whether link $e$ is available under scenario $ \mathbf{z}$, 
then we have 
\begin{equation}
f^{t}_{d} \ge 0, \quad\forall d \in \hat{D} ,  k\in K,  t\in T^{\mathbf{z}}_k.
\label{constraint-f3}
\end{equation}
and 
\begin{small}
\begin{eqnarray} \label{B-constraint}
\sum_{d\in \hat{D}}\sum_{k\in K, t\in T^{ \mathbf{z}}_k} f^{t}_{d}u_t^e \le c_e \times w_e^{ \mathbf{z}}, \forall e \in E
\end{eqnarray}
\end{small}

Finally, the failure recovery scheme tries to maximize the total profit (after refunding) by

\begin{equation}
\small
\begin{aligned} \label{BATE-recovery}
 &maximize  \sum_{d\in \hat{D}} r_d\\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t.  (\ref{constraint-f3}), (\ref{B-constraint}), (\ref{B-return}), (\ref{A-SSS2})
\end{array}
\end{aligned}
\end{equation}

This mixed-integer linear programming  (MILP) problem can be proved to be NP-hard, 
and the proof details can be found in Appendix \ref{appendix1}.
To efficiently solve this problem, we further propose a 2-approximation greedy algorithm.
The key idea is to prioritize demands by the ratio of profit to the allocated bandwidth in a non-decreasing order.
Due to space limitations, the detailed algorithm, as well as the proof on its optimality, 
are put into Appendix \ref{B}}.

\iffalse
\begin{lemma}\label{NP-hard}
The failure recovery problem is NP-hard.
\end{lemma}
The detailed proof can be found in Appendix \ref{appendix1}.

%For the second challenge, although the powerful mathematical optimization solver such as Gurobi \cite{gurobi} can derive the solution, it might be too slow to converge before next TE scheduling epoch.
In this case,  we propose a greedy algorithm to attain an approximate solution whose pseudocode is shown in Appendix \ref{B}.
The key idea of the greedy algorithm is to give priority to demands in non-decreasing order by the ratio of profit to its efficient bandwidth demands.
\textit{We also prove the approximation of the greedy algorithm is 2  in Appendix \ref{B}}. 
%The greedy algorithm can solve $\mathsf{BATE}$  problem in  $O(|J||Z||T_k||E|)$ time.
%We further explore the accuracy of greedy algorithm in Section \ref{evaluation}.
\false
